AA Distributed Software Development Methodology

### 2013-02-18 paper.tex
mais mudancas

In one month, each developer contributed to many very large free software
projects. Many of the developers started the training with no
knowledge of what is free software and ended that period becoming a
free software developer.

>>>>

In one month, each developer officially contributed to one or many free software
projects. Many developers started the initiation training with no knowledge of what
is free software and ended that period becoming a free software developer.
